---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(
  tibble.print_min = 5,
  tibble.print_max = 5
)
Sys.setenv(TZ = "America/Detroit")
```

# lubridateExtras <img src="man/figures/logo.svg" align="right" height="120" width="139" />

Convenience functions for the lubridate package

<!-- badges: start -->
[![R build status](https://github.com/HaydenMacDonald/lubridateExtras/workflows/R-CMD-check/badge.svg)](https://github.com/HaydenMacDonald/lubridateExtras/actions)
<!-- badges: end -->

## Overview

Lubridate makes it easier to work with date-time data in R and provides new capabilities. LubridateExtras builds on top of lubridate to provide a number of convenience functions, primarily focused on abstracting patterns in ways that improve code readability and reduce copying and pasting code.

## Installation

```{r, eval = FALSE}
# lubridateExtras is not currently on CRAN
# Please install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("ellisvalentiner/lubridateExtras")
```

If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/ellisvalentiner/lubridateExtras/issues).

## Usage

```{r}
library(lubridateExtras)

yesterday()

tomorrow()

days_ago(7)  # equivalent to lubridate::today() - lubridate::days(7)

days_hence(7)  # equivalent to lubridate::today() + lubridate::days(7)

hms("2017-10-22 15:33:00")  # extracts the time-of-day component
```

## Why lubridateExtras?

Some people are probably asking the question: why lubridateExtras?

lubridateExtras does not do anything that you cannot do with lubridate but similarly you don't need lubridate at all to work with date/times in R! If you like the syntactic sugar of lubridateExtras then use it, otherwise stick with what works for you.
